### 2018-02-28 thesis/contents/reviews/machine-learning.tex
Updates from ShareLaTeX

\section{Machine Learning}
Machine learning (ML) is a branch of computer science that aims to learn and form predictions from data. In contrast with static algorithmic programming, where the structures of the algorithms are predefined, machine learning approaches construct models based on observed data, in order to extend its predictions to the unobserved. Strategies and algorithms for constructing various models overlap with the fields of artificial intelligence, computational statistics, pattern recognition, and neuroscience. Advanced in modern machine learning, especially in deep neural networks \cite{LeCun2015}, in recent years have led to wide spread adaptation of machine learning based online services in translation \cite{bahdanau2014neural}, image search \cite{simonyan2014very}, and speech recognition \cite{graves2013speech}. There is also surging interest in deploy machine learning systems in radiology and disease diagnosis in medicine\cite{Kamnitsas2016,Suk2014}.

>>>>

\section{Machine Learning}
Machine learning (ML) is a branch of computer science that aims to learn and form predictions from data. In contrast with static algorithmic programming, where the structures of the algorithms are predefined, machine learning approaches construct models based on observed data, in order to extend its predictions to the unobserved. Strategies and algorithms for constructing various models overlap with the fields of artificial intelligence, computational statistics, pattern recognition, and neuroscience. Advanced in modern machine learning, especially in deep neural networks \cite{LeCun2015}, in recent years have led to wide spread adaptation of machine learning based online services in translation \cite{Bahdanau2014a}, image search \cite{simonyan2014very}, and speech recognition \cite{graves2013speech}. There is also surging interest in deploy machine learning systems in radiology and disease diagnosis in medicine\cite{Kamnitsas2016,Suk2014}.
